Blocking-resistant communication through high-value web services

### 2014-05-13 docs/meek.tex
make figures appear in the center
Move CloudFront to other deployment.

\begin{figure}
\includegraphics[width=\linewidth]{architecture}
\caption{
System architecture.
The Google frontend server is the server that dispatches requests to different services depending on the Host header.
Components that are new in our system are outlined in blue.
The ``Google infrastructure'' block may be replaced by other infrastructure that supports domain fronting.
}
\label{fig:architecture}
\end{figure}

@@

\begin{figure}
\includegraphics{browser-architecture}
\caption{
Client architecture including a browser extension for TLS camouflage.
Dashed lines show the process hierarchy.
Solid lines show the flow of outgoing communication.
The headless instance of the browser runs in the background and is invisible to the user.
This figure is a detailed view of the ``User's PC'' component of Figure~\ref{fig:architecture}.
}
\label{fig:browser-architecture}
\end{figure}

@@

\section{Other third-party services}
\label{sec:otherservices}

A censor can block meek by blocking access to Google entirely.
To take such a step is extreme, because of its high collateral damage,
but it is not outside the realm of possibility.
% Cite when Google and Gmail were completely blocked temporarily.
We investigated how easily our system can be adapted to hard-to-block systems other than Google,
and found that CloudFlare, a content delivery network, in principle supports domain fronting.

CloudFlare provides the frontend of $X$ web sites, $Y$ of them supporting HTTPS~\cite{something}.
CloudFlare supports the domain fronting trick;
that is, it is possible that a request has one domain in the TLS layer
and another in the HTTP layer, and the CloudFlare server will transparently redirect it to proper place.
While we verified that domain fronting would work on CloudFlare,
we did not test deployment,
because when we asked we were told that our planned use would be against CloudFlare's terms of service.
CloudFlare hosts a number of HTTPS sites.
Choosing just one of them to be the front in TLS connections could cause
the innocent third-party domain to be censored even though it is not itself carrying any circumvention traffic.
To avoid this problem, the front can be simply a CloudFlare IP address,
with no SNI at all.
The censor then faces the choice of allowing circumvention traffic,
or else blocking a large number of popular unrelated web sites.

We were not able to make the system work with Amazon CloudFront nor Akamai.
% Dreamhost? Other HTTPS webhosts with PHP bridge?

@@

>>>>

\begin{figure}
\centering
\includegraphics[width=\linewidth]{architecture}
\caption{
System architecture.
The Google frontend server is the server that dispatches requests to different services depending on the Host header.
Components that are new in our system are outlined in blue.
The ``Google infrastructure'' block may be replaced by other infrastructure that supports domain fronting.
}
\label{fig:architecture}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{browser-architecture}
\caption{
Client architecture including a browser extension for TLS camouflage.
Dashed lines show the process hierarchy.
Solid lines show the flow of outgoing communication.
The headless instance of the browser runs in the background and is invisible to the user.
This figure is a detailed view of the ``User's PC'' component of Figure~\ref{fig:architecture}.
}
\label{fig:browser-architecture}
\end{figure}

@@

@@

A censor can block meek by blocking access to Google entirely,
but other systems can take the place of Google.
An attractive alternative is CloudFlare, a large content delivery network,
which supports domain fronting, dispatching requests based on the Host header
rather than IP or SNI.
We did not test deployment on CloudFlare,
because their terms of service are not clear on whether this kind of use is allowed,
and we got an ambiguous answer when we asked for clarification.
A particular concern when using CloudFlare or other content delivery networks is the choice of front domain.
If one domain is being used particularly as a front for circumvention traffic,
it may find itself blocked by the censor, even though it is not itself
involved in any circumvention.
One good solution to this problem may be not to use a domain name at all,
but only the IP address of one of CloudFlare's servers.
The censor will then face the choice of allowing circumvention traffic,
or else blocking a large number of unrelated web sites.

% We were not able to make the system work with Amazon CloudFront nor Akamai.
% Dreamhost? Other HTTPS webhosts with PHP bridge?
